Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology

### 2014-08-07 paper.tex
Added ipython notebook, updated water profile section and produced p

    The remainder of this work is presented as follows.
    In section \ref{sect:streamingCell} we build and measure a simple streaming potential cell.
    We confirm the relationship between pressure and applied pressure and investigate the effect of channel height.
    In section \ref{sect:waterConsumption} we estimate a typical domestic water usage profile.
    This consumption profile will be used as the basis for estimating the amount of energy available to the harvester.
    Section \ref{sect:powerRequirements} determines the amount of energy an electronic meter would need to be useful.
    Following on this, section \ref{sect:harvesterSize} presents the required dimensions a usable harvester would need.
    In section \ref{sect:results} we present the results of our measurements and quantify our predictions.
    And finally, we discuss the feasibility of the streaming cell harvester in the conclusion.

@@

    We replicate the fabrication method and approximate dimensions of \cite{Gu2000} to produce ten streaming cell channels.
    The internal dimensions of which are \SI{3}{\centi\metre} long, \SI{1}{\centi\metre} wide and heights in the range of \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
    These dimensions are directly comparable to those of \cite{Gu2000}, where the length and width are the same but the heights span a wider range.
    The channels themselves are made from glass microscope slides (Sail Brand - JIA 7101WT) which are sectioned into halves.
    Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to create the channels.
    The dimensions at each end of each channel have been measured under a microscope to determine the actual channel height.

@@

    \section{Estimation of Typical Household Water Consumption}:
    \label{sect:waterConsumption}
    In \cite{Heinrich2007} the author monitors the water consumption of twelve homes throughout the Kapiti Coast, New Zealand over a period of eight months.
    From that study the following metrics were found:
    \begin{itemize}
    \item Toilet
    \item Washing Machine
    \item Bath
    \item Taps
    \end{itemize}

    \section{Estimation of Power Requirements}
    \label{sect:powerRequirements}
    \section{Estimation of Streaming Cell Harvester}
    \label{sect:harvesterSize}

>>>>

    The remainder of this work is presented as follows.
    In section \ref{sect:streamingCell} we build and measure a simple streaming potential cell.
    We confirm the relationship between pressure and applied pressure and investigate the effect of channel height.
    In section \ref{sect:waterConsumption} we estimate the amount of harvestable energy from a constructed domestic water usage profile.
    Section \ref{sect:powerRequirements} quantifies energy requirements of a simple electronic meter.
    {\color{blue} next two sentences ignore.}
    Following on this, section \ref{sect:harvesterSize} presents the required cell dimensions to  harvester capable of producing the requisite energy needs.
    In section \ref{sect:results} we present the results of our measurements and quantify our predictions.

    And finally, we discuss the feasibility of the streaming cell harvester in the conclusion.

@@

    We replicate the fabrication method and approximate dimensions of \cite{Gu2000} to produce ten streaming cell channels.
    The internal dimensions of which are \SI{3}{\centi\metre} long, \SI{1}{\centi\metre} wide and heights in the range of \SI{25}{\micro\metre} to \SI{250}{\micro\metre}.
    These dimensions are directly comparable to those of \cite{Gu2000}, where the length and width are the same but the heights span a wider range.
    The channels themselves are made from glass microscope slides (Sail Brand - JIA 7101WT) which are sectioned into halves.
    Plastic shims (Garlock Colorplast) are epoxied (Selleys Araldite Ultra Clear Resin) between slide halves to create the channels.
    The dimensions at each end of each channel are measured under a microscope to determine the actual channel height.

@@

    \section{Estimation of Harvestable Energy From A Typical New Zealand Dwelling}
    \label{sect:waterConsumption}
    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{graph_profile.pdf}
        \end{center}
        \caption{Sample profile showing constructed instances of washing machine use, a shower and a toilet flush.
        Washing machine usage is broken into two parts corresponding to a wash and rinse cycle.}
        \label{fig:profileSample}
    \end{figure}

    In \cite{Heinrich2008} the authors monitor water consumption of 51 homes throughout Auckland, New Zealand between February and September of 2008.
    The report shows that the majority of domestic water is consumed by the shower (30\%), washing machine (27\%) and toilet (20\%).
    Together these account for over three quarters of the indoor water usage in the average home.
    We have created a flow profile from which to calculate the available harvestable energy using data from both \cite{Heinrich2008} and \cite{Heinrich2007}.
    The profile fits the usage statistics of a home with two occupants according to the previously mentioned reports over the duration of a week.
    The during that time five usages of a washing machine, fourteen showers and fifty six toilet flushes occur.
    A sample of the usage profiles of each item is shown in Fig. \ref{fig:profileSample}

    Informal investigation (Internet search) shows that a common brand of water meter in the Auckland region is the Kent
    \section{Estimation of Power Requirements}
    \label{sect:powerRequirements}
    \section{Estimation of Streaming Cell Harvester}
    \label{sect:harvesterSize}
